---
title: "Narrative"
author: Krista Waugh
output: github_document
---

According to this [article](https://sircharlesincharge.com/2019/03/13/golden-state-warriors-serious-concern/) in *Fansided*, the Golden State Warriors main weakness is their defense, as the demonstrated in their recent loss against the Phoenix Suns. It is hard to admit that the Bay Area's beloved Warriors may have any weakness at all, so I wont. Here I have analyzed only the shooting percentages of the Warriors offensive players from their legendary 2016/2017 season. Is this a thorough analysis of the Warriors overall performance as a team? Not particularly, but it does bring to light some of what makes them one of the most talked about teams in NBA history: their undeniably high shooting success rates. 

The two years prior to the 2014/2015 season, the Warriors finished 6th in the league, and before that from the mid 90s until their 6th place finish in 2013, they were hanging out around 10th place overall. The 2016/2017 season was Kevin Durant’s first season with the Warriors, after playing for Oklahoma City Thunder for nine seasons, experiencing some tough losses to the Warriors during the Finals, and ultimately never winning a finals with OKC Thunder. Stephen Curry, Klay Thompson, Draymond Green, and Andre Iguodala are some of the most famous names in this new wave of Warriors fame, from what I understand as someone who sat through their first basketball game in the spring of 2015, along with what seems like the great majority of today’s Warrior fans. 

Understandably so, as the Bay Area is such a hub of technology, food, and entertainment- the Warriors had to be the best in order to take the spotlight among all the other stimulation present in the area. The sports industry is ultimately a business, and the number of Warriors jerseys sported around town during May and June indicate that business is booming. This can be attributed almost completely to how fun these men are to watch. People like basketball probably for a lot of reasons, but a big one is how fast paced it is. If you leave the room to grab a beer you will have missed something, unlike soccer or football. Being a Warriors fan for the sake of entertainment is great because they keep shooting and keep making it, which is what my analysis is centered around: shooting percentages. 


The purpose of this report is to take a closer look at shooting success rates, while keeping in mind the *business* of basketball, not just the game.  Earlier in the semester, my class (Stat 133 at UC Berkeley) discussed the “cost per point” factor of players. You want better players on your team, but then you have to pay them more. We don’t take a deep look at salary vs points in this analysis but during the time I spent working on this project I pondered whether as an NBA team owner, would you  prefer players who win games with consistent and unrelenting shooting success close to the net, or players who make the crowd go wild with crazy three pointers? Do you want predictability of winning or do you want to work from more of an entertainment industry standpoint? Who ultimately makes more money for the Warriors, and is that the same player who gets paid the most by the Warriors? Here are the salaries of the top 5 highest paid players for the 2016/2017 season. Durant is at the top, and he does have the overall highest success rate, but Thompson leads in three pointers and Iguodala leads in two pointers, while Curry earns the Warriors the most total points. 

Player  | Salary
------------- | -------------
Kevin Durant |	$26,540,100
Klay Thompson |	$16,663,575
Draymond Green |	$15,330,435
Stephen Curry |	$12,112,359
Andre Iguodala |	$11,131,368

 

While Kevin Durant, Stephen Curry, and Klay Thompson might be the most widely known for their shooting skills, Andre Iguodala actually has the highest percentage of two point field goals made of the five players included in this analysis, with a 63.8% success rate, with Kevin Durant behind him at 60.6%.However, Durant leads the team with his overall percentage, which includes three pointers. Klay Thompson has the best three-pointer success rate at 42.2%. 

The full set of shooting percentages for the five players can be seen below, caption options seem to only be useful for knitting HTML and Latex. The first table is **"Effective 2 Pointer Shooting % by Player"**, the second is **"Effective 3 Pointer Shooting % by Player"**, and the third is **"Effective Total Shooting % by Player"**. 


```{r echo=FALSE, results='hide'}
shots2pt <- matrix(c("Curry","563","304", "53.99%","Durant", "643","390","60.6%","Green", "346","171","49.4%", "Iguodala", "210", "134", "63.8%", "Thompson", "640", "329", "51.4%"), ncol=4,byrow=TRUE)
colnames(shots2pt) <- c("name","total","made", "perc_made")
table_shots2pt <- as.table(shots2pt)
table_shots2pt
   
shots3pt <- matrix(c("Curry","687","280", "40.7%","Durant", "272","105","38.6%","Green", "232","74","31.9%", "Iguodala", "161", "58", "36%", "Thompson", "580", "246", "42.4%"), ncol=4,byrow=TRUE)
colnames(shots3pt) <- c("name","total","made", "perc_made")
table_shots3pt <- as.table(shots3pt)
table_shots3pt

shots_total <- matrix(c("Curry","1250","584", "46.7%","Durant", "915","495","54.1%","Green", "578","245","42.4%", "Iguodala", "371", "192", "51.8%", "Thompson", "1220", "575", "47.1%"), ncol=4,byrow=TRUE)
colnames(shots_total) <- c("name","total","made", "perc_made")
table_shots_total <- as.table(shots_total)
table_shots_total


```

```{r echo=FALSE}
df2pt <- knitr::kable(table_shots2pt, row.names = FALSE, caption = "Effective 2 Pointer Shooting % by PLayer", format = 'pandoc')
df2pt
```

```{r echo=FALSE}
df3pt <- knitr::kable(table_shots3pt, row.names = FALSE, caption = "Effective 3 Pointer Shooting % by PLayer", format = 'pandoc')
df3pt
```

```{r echo=FALSE}
df_shots_total <- knitr::kable(table_shots_total, row.names = FALSE, caption = "Effective Shooting % by Player", format = 'pandoc')
df_shots_total
```



Based on the charts, we can assume that total points earned for the team isn’t the biggest deciding factor when it comes to salary, as Durant’s salary is more than Double Curry’s, the top scorer. Admittedly, since it was Durant’s first season the Warriors probably had to give him a good deal. His previous salary with Oklahoma City Thunder was just under $22 million.  But is Durant worth twice as much to the Warriors business as Stephen Curry? Not anymore. The reason for Curry’s “low” salary was because he was still under his first contract with the Warriors for 44 million from 2012 through the 2016/2017 season. Curry renewed his contract with the Warriors (yay!) and will now make $201 million over five years, making him the highest paid NBA player. 


While Curry’s shooting success percentage isn’t the highest of all of all the Warriors, he ultimately earns the most points overall and the most three pointers, but sits in third place in the Warriors lineup for two pointers. From a business standpoint, Stephen Curry is an investment because he consistently wins games and plays up the entertainment industry of basketball with his amazing shots, which is probably why his shooting percentage is slightly lower than it seems during a game. 


